---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wbData

<!-- badges: start -->
<!-- badges: end -->

Personal package to easily download and use Wormbase data. At this point, it only downloads the "geneIDs" table and provides function to convert between Wormbase IDs and gene symbols. I may add functions to download and access GTF files later.

The three advantages are:

* finding files for any given Wormbase release (even though the actual path changes)
* keeping all these files in a single place
* facilitating common operations.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AlexWeinreb/wbData")
```
## Example

To load the geneIDs table for Wormbase release WS277 and convert between gene ID and gene symbol:

```{r convert_id}
library(wbData)

gids <- wb_load_gene_ids("WS273")
s2i("unc-10", gids)
i2s(c("WBGene00006752", "WBGene00004412"), gids)
```

The downloaded file is stored on the local computer to avoid re-downloading every time. The cache can be emptied as follows:

```{r clean}
wb_clean_cache(273)
```
